---
title: Analysing the data
author: Julien Colomb
date: '2018-07-05'
slug: analysing-the-data
categories:
  - material
tags:
  - RDM
  - CC0
---

# argument_analysis

On this page, we will report the analysis of the data we gathered and collected, the page is recreated with updated data. The data itsel is created in a spreadsheet available on the github page.

```{r, echo=FALSE, warning=FALSE, results='hide'}

library (tidyverse, quietly = TRUE, warn.conflicts = FALSE)

argument_analysis <- read_delim("../../static/material/CC0/argument_analysis.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE,
    col_types = cols(
  ID = col_integer(),
  Argument = col_character(),
  type_of_col = col_character(),
  `linked to` = col_character(),
  content = col_character(),
  source_intern_slug = col_character(),
  source_extern = col_character()
)
) 

```


`r # We split that data into one table for each argumentation.`

For each argument, we gathered 

- real life stories
- punch lines
- jokes, funny way to bring it
- reference to the (pop) culture wich could be used

# list of arguments:

```{r, echo=FALSE, results='asis'}
print(unique(argument_analysis$Argument))
```

# details

```{r, run-numeric-md, include=FALSE}
argument_analysis$source_extern = 
  paste0 ('<a href="',argument_analysis$source_extern,'" target="_blank">',argument_analysis$source_extern,"</a>")

argum = unique(argument_analysis$Argument)
out = NULL
for (thisargument in  argum){
  
  #cat (paste0("## ",thisargument, " <br>"))
  #print (nrow (table))
  #print(htmltools::tagList(DT::datatable(table)))
  #out = c(out, knitr::knit_expand('../../template_analysis.rmd'))
  out = c(out, knitr::knit_expand('../../template_analysis.rmd'))
}
```


`r paste(knitr::knit( text= out), collapse = '\n')`

